Turbulence in compact to giant HII regions

### 2022-05-06 strucfunc_paper.tex
Unfinished changes
Minor changes to strucfunc descriptions

\subsection{Example results of model fitting to the Orion Nebula}
\label{sec:example-results-orion}

This dataset is among the highest quality of those in our sample,
with more than \num{e5} spatial points and a factor of more than \num{500}
between the smallest and largest separations.
As a result, the observationally derived structure function (Figure~\ref{fig:strucfunc-fit-Galactic}a)
is very smooth and the model fit is very well constrained,
as evidenced by the tight credibility limits on the model parameters.
The derived correlation length \(r_0 = \SI{0.068}{pc}\) is \num{7} times smaller
than the box size, which indicates that there should be a moderate finite map effect
(section \ref{sec:effects-observ-limit-large} and Appendix~\ref{sec:finite-box-effects}),
but it is well within the range where the model fit can give reliable measurements
(see Figure~\ref{fig:finite-box-effect}).
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\) is more than \num{30} times smaller
than \(r_0\), meaning that the seeing has a negligible effect at the correlation scale and above.

Figure~\ref{fig:corner-example-Orion} shows the covariances
between parameters in the model fit.

@@

>>>>

\subsection{Example results of model fitting to the inner Orion Nebula}
\label{sec:example-results-orion}

This dataset is among the highest quality of those in our sample,
with more than \num{e5} spatial points and a factor of more than \num{500}
between the smallest and largest separations.
As a result, the observationally derived structure function (Figure~\ref{fig:strucfunc-fit-Galactic}a)
is very smooth and the model fit is very well constrained,
as evidenced by the tight credibility limits on the model parameters.
The derived correlation length \(r_0 = \SI{0.068}{pc}\) is \num{7} times smaller
than the box size, which indicates that there should be a moderate finite map effect
(section \ref{sec:effects-observ-limit-large} and Appendix~\ref{sec:finite-box-effects}),
but it is well within the range where the model fit can give reliable measurements
(see Figure~\ref{fig:finite-box-effect}).
The derived seeing parameter \(s_0 = \SI{0.002}{pc}\) is more than \num{30} times smaller
than \(r_0\), meaning that the seeing has a negligible effect at the correlation scale and above.
Figure~\ref{fig:corner-example-Orion}  shows  the covariances  between
parameters  in the  model fit,
which in some cases show significant correlations.
For example, \(\sigma^2\) and \(r_0\) are positively correlated,
whereas \(m\) and \(s_0\) are negatively correlated.

@@

The structure functions for the remaining Galactic sources
are shown in Figure~\ref{fig:strucfunc-fit-Galactic}b--d.
The data quality for these sources is considerably worse than for the inner Orion Nebula.

while those in the Magellanic Clouds are shown in Figure~\ref{fig:strucfunc-fit-MC}
and those in more distant galaxies in Figure~\ref{fig:strucfunc-fit-ExtraGal}.
